Performance Comparison of Common Face Detection APIs using Video Stills from Professional Tennis Matches

### 2018-02-16 paper/paper.Rmd
Validation and resultsection included

##Results

@@

### Modeling detection rate

A logistic regression model was used to assess the characteristics of the face and scene that may have affected the detection likelihood of the face. A step-wise variable selection method was used to find variables of significance for any of the APIs. The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments. Variables that were not included denoted whether there was a graphic or live shot visible, the role of the person whose face was captured and whether or not there was a person in the image.
detect
A separate model was fit using the faces for each API.

@@

For the most part, the APIs were all affected by the same factors. Those that negatively affected all APIs were glasses, visor or hat. Background only negatively affected Google's detection rate. Situation had different effects on each API.
Results for Google were most interesting in the shot angle had differing effects on the detection.

```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API. The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match all contribute to the struggle of the APIs.\\label{fig:UnlikelyFace}", dev="jpeg", dpi=300}

@@

When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.

### Detection rates and API comparison

>>>>

##  Validation

Descriptive statistics were used to discern differences in the performance of the four APIs. These are presented in tables and plots and discussed in the results section.
A logistic regression was used to study the effect of conditions and accessories on the detection performance of the APIs.

## Regression Analysis

A logistic regression model was used to assess the characteristics of the face and scene that may have affected the detection likelihood of the face. A step-wise variable selection method was used to find variables of significance for any of the APIs. The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments. Variables that were not included denoted whether there was a graphic or live shot visible, the role of the person whose face was captured and whether or not there was a person in the image. 
A separate model was fit using the faces for each API.

# Results

@@

## Modeling detection rate

@@

For the most part, the APIs were all affected by the same factors.
The factors that negatively affected all APIs were glasses, visor or hat. Background only negatively affected Google's detection rate. Situation had different effects on each API.
When the shot angle was considered in conjunction with the background the results for Google showed there was a positive effect on detection rate of faces in all circumstances. There was no significant impact on the other APIs.

```{r UnlikelyFace, fig.cap = "The face captured manually in this image was not captured by any API. The head angle, shot angle, lighting, wearing the visor and being captured across the court during the match are all associated with lower rates of detection.\\label{fig:UnlikelyFace}", dev="jpeg", dpi=300}

@@

When forcing no intercept, all variables are significant at the 0 level, and obscured was significant for all four up to the 0.01 level.

## Detection rates and API comparison
